Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality

### 2025-02-13 Manuscript.qmd
Update manuscript

  | The growing visibility of the LGBTQ+ community is accompanied by the flourishing of queer characters in media in the information era. While previous studies have explored the double-edged impact of queer media representation on LGBTQ+ individuals’ development, few have compared these effects across different LGBTQ+ subgroups. This study investigates queer media characters’ psychological impacts on LGBTQ+ individuals with different identities, examining the relationship between perceived character authenticity, intersectionality, and characters’ impacts on LGBTQ+ individuals’ psychological well-being using a reliable survey instrument in a worldwide sample.

  | Findings revealed that marginal groups within the LGBTQ+ community, including those from developing countries, gender minorities, and racial minorities, reported higher scores about queer media characters’ positive impacts on psychological well-being compared to their mainstream counterparts. However, in terms of sexual orientation, mainstream groups (i.e., gay and lesbian respondents) showed higher scores. Importantly, the study found strong positive correlations between authenticity ratings, intersectionality ratings, and scores of queer characters’ positive impacts on psychological well-being.

@@

The current study examined queer media characters’ impacts on LGBTQ+ individuals’ psychological well-being through two overarching research questions. The first research question investigated whether there were differences in queer characters’ psychological impacts among LGBTQ+ individuals with different identities. Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, races, ages, and residential countries on queer characters’ psychological impacts. Given the fact that there were still queer stereotypes and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents). The second research question asked whether queer media consumption patterns, perceived character authenticity, and perceived character intersectionality can predict queer media characters’ psychological impacts. Specifically, this study hypothesized that lower ratings for perceived character authenticity and intersectionality would result in lower ratings for queer characters’ positive psychological impacts. Conversely, higher ratings for perceived character authenticity and intersectionality would result in higher ratings for queer characters’ positive psychological impacts.

@@

### Reliability Tests
Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (see Table 1). Cronbach's alpha coefficients were calculated for each scale. Specifically, the authenticity rating measurement demonstrated satisfactory reliability (α = 0.76). The intersectionality rating measurement showed excellent reliability (α = 0.91). Both the media individual development scale and the media community belonging scale exhibited excellent reliability (α = 0.96 for both). The emotional well-being measurement also demonstrated excellent reliability (α = 0.96). Finally, the overall psychological well-being measurement showed the highest reliability with an excellent Cronbach's alpha of 0.98. These results indicate that all scales used in this study have good to excellent internal consistency, suggesting they are reliable measures of their respective constructs.

@@

### Respondent Characteristics
167 respondents were eligible for the data analysis after data cleaning. Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old. The average age of the sample was `r round(mean(queer.hypo$age), 1)` years old (*SD* = `r round(sd_age, 1)`). This wide age range ensured the study captured perspectives from individuals across different generations. Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective. Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as non-binary, genderfluid, gender non-conforming, or agender. Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender. The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (Figure 2). The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native. This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersecting identities.

@@

One-way ANOVA results showed that there were no significant differences or directional effects in queer media characters’ psychological impacts among different generations (*p* = .70) or between transgenders and non-transgenders (*p* = .25). However, significant differences were found between developed and developing countries' residents (Figure 3). Specifically, residents in developed countries showed lower psychological impacts scores by queer media characters than those in developing countries ($M_{\text{developed}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developed"]), 2)`$ vs. $M_{\text{developing}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developing"]), 2)`$; *F*(`r summary_country_effect$Df[1]`, `r summary_country_effect$Df[2]`) = `r round(summary_country_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_country_effect$"Pr(>F)"[1])`).

Though the ANOVA result did not show significant differences among different gender identities, there was a directional effect indicated by the violin plot (Figure 4). Specifically, men showed lower psychological impacts scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs. $M_{\text{womenother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Women, or nonbinary, or agender"]), 2)`$; *F*(`r summary_gender_effect$Df[1]`, `r summary_gender_effect$Df[2]`) = `r round(summary_gender_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_gender_effect$"Pr(>F)"[1])`). The distribution also indicated that men have more low scores than their women or nonbinary counterparts. Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations, but there was also a directional effect (Figure 5). Specifically, bisexual individuals showed the lowest psychological impacts scores among all sexual orientations, while gay or lesbian had the highest impacts scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).

@@

Racial differences in queer media characters’ psychological impacts were marginally significant (Figure 6). Specifically, white respondents showed lower psychological impacts scores than other racial groups ($M_{\text{white}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "White"]), 2)`$ vs. $M_{\text{blackother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "Black, Asian, Indian, and Others"]), 2)`$; *F*(`r summary_race_effect$Df[1]`, `r summary_race_effect$Df[2]`) = `r round(summary_race_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_race_effect$"Pr(>F)"[1])`).

```{r}
#| label: fig-plot-race-psych-impact
#| fig-cap: Race Comparison of Queer Characters' Psychological Impacts
#| fig-width: 10
#| fig-height: 5
# Visualization: Violinplot
race_effect_boxplot <- ggplot(queer.hypo, aes(race_category, psychological_wellbeing_score)) + 
  geom_boxplot(aes(fill = race_category)) +
  theme_bw() +
  scale_fill_manual(values = c("#cfb5a0","#f1e2c8")) +               
  scale_colour_manual(values = c("#cfb5a0","#f1e2c8")) + 
  labs(title = "Race Comparison of Queer Characters' Psychological Impacts", 
       x = "Racial Identity", y = "Queer Characters' Psychological Impact Score") +
  theme.clean()+
  theme(axis.text.x = element_text(hjust = 0.5))+
  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
  stat_summary(fun = mean, geom = "point", color = "white", size = 3, shape = 18, 
               position = position_dodge(0.75), aes(shape = "Mean"), 
               show.legend = FALSE) +  
  stat_summary(fun = mean, geom = "text", aes(label = round(after_stat(y), 2)), 
               color = "white", vjust = -1, position = position_dodge(0.75), 
               size = 4, show.legend = FALSE) +
  labs(fill = "Racial Identity")

@@

Figure 10 indicates that the authenticity rating positively predicts psychological well-being scores for all gender identities. The regression line for men is steeper, indicating that the authenticity rating has a stronger effect on psychological wellbeing scores for men. Nevertheless, given the fact that men have lower psychological impacts scores, the authenticity rating may not be the only factor influencing psychological impact scores.

@@

Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low scores for both ratings. This result suggests that bisexual respondents' low psychological impacts scores may be related to the perceived authenticity of queer media characters.

@@

```{r}
#| label: fig-plot-auth-psych-impact-race
#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Racial Identity
#| message: false
#| fig-width: 11.5
#| fig-height: 5.5

@@

Linear regression results also indicated a significant effect of queer character intersectionality rating on psychological wellbeing impact scores (*F*(`r df1_inter`, `r df2_inter`) = `r round(f_statistic_inter, 2)`, *p* `r if(p_value_inter < .001) "< .001" else paste("=", round(p_value_inter, 3))`). The $R^2$ was `r round(r_squared_inter,3)`, indicating that the perceived queer character authenticity explained `r round(r_squared_inter * 100, 1)`% of the variance in psychological wellbeing scores. This robust association suggests that LGBTQ+ individuals who perceive queer media characters as more intersectional tend to experience more positive psychological outcomes.

@@

```{r}
#| label: fig-plot-inter-psych-impact-country
#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Country
#| message: false
#| fig-width: 10
#| fig-height: 5

@@

The results of the study indicated that queer media characters' psychological impacts on LGBTQ+ individuals did not significantly differ among different generations. This finding suggests that queer media representations may have become more diverse in age over time, catering to different generations of LGBTQ+ individuals. It is also consistent with @dhoest_queer_2022, which found that LGBTQ+ individuals across all generations were keen to watch LGBTQ-themed films and rated TV shows featuring LGBTQ+ characters as important. The recent years' increase in transgender media representation may have contributed to the positive psychological impacts on transgender individuals, resulting in the insignificant differences between transgender and non-transgender individuals. For instance, the number of transgender characters on broadcast TV increased from two characters in 2014 to 24 characters in 2024 [@GLAAD2024]. Reality shows such as *RuPaul's Drag Race* and TV series like *Pose* and *Euphoria* were also popular among transgender participants in this study.

The study has also found that queer media characters' psychological impacts on LGBTQ+ individuals were less significant for individuals living in developed countries than for those living in developing countries. A plausible explanation could be a higher saturation of queer characters in media leading to a normalization of queer identities in developed countries. As a result, the impact of individual characters may be less pronounced, as audiences become desensitized to their presence. In contrast, the scarcity of queer characters in developing countries may lead to a more profound impact when they appear. Additionally, LGBTQ+ individuals in developed countries might have more access to mental health resources and support systems (e.g., LGBTQ+ advocacy groups), which could mitigate the effects of media representations on psychological well-being. Nevertheless, LGBTQ+ individuals in developing countries may rely more on cultural resources such as queer media characters for representation and community belonging, leading to a stronger psychological impact.

Regarding gender identity and racial identity, the study found that queer media characters' psychological impacts on LGBTQ+ individuals were more positive for gender and racial minorities. These findings reflected that queer media representations have become more diverse in gender and racial identities. Specifically, @GLAAD2024 reported 2024 as the fifth year there were more LGBTQ+ women than men on broadcast, with 58% were women or nonbinary, and 42% were men. Regarding racial identity, the number of LGBTQ+ characters of color on broadcast TV increased from 23% in 2014 to 50% in 2024, with 30% of LGBTQ+ characters being Black, 7% Latine, 5% Asian, and 8% multiracial or others. This shift in decades of LGBTQ+ representation may have contributed to the more positive psychological impacts on gender and racial minorities.

Nevertheless, the study found that regarding sexual orientation, the mainstream group (i.e., gay or lesbian) had the highest psychological impact scores, while bisexual respondents had the lowest. This is consistent with @GLAAD2024's report that the percentage of bisexual characters on broadcast TV was significantly lower than the percentage of bisexual as the majority in the LGBTQ+ community (24% vs. 58%). Apart from this disparity, the bi+ erasure (i.e., the tendency to not specify a character as bisexual) in media may have also contributed to the lower psychological impact scores on bisexual respondents. The following section further discusses the potential explanations from the perspectives of perceived character authenticity and intersectionality.

@@

This study found that the frequency of queer media exposure and discussion engagement may predict psychological impacts. Specifically, the results indicated that more respondents in developed countries had lower exposure to queer media characters (e.g., a few times per year), which may contribute to lower psychological impact scores. This finding suggests that the normalization of queer characters and more well-established social support systems for LGBTQ+ individuals in developed countries may have led to a desensitization effect, reducing the psychological impacts of queer characters. Regarding queer media discussion engagement, the results revealed that women and nonbinary individuals had higher discussion engagement than men, which may contribute to higher community belonging scores and overall psychological impact scores. This finding also highlights that there may not be enough online forums or platforms specifically tailored to the needs and interests of queer men. Additionally, social norms and expectations around masculinity may discourage queer men from openly discussing their experiences or engaging in vulnerable conversations that reveal their identities. These norms often penalize emotional expressiveness in men, which might make them less likely to participate in discussions that require self-disclosure, resulting in lower community belonging scores.

The study also revealed that perceived queer character authenticity and intersectionality are strongly positively related to queer characters' psychological impact scores. The more authentic and intersectional LGBTQ+ individuals perceive queer media characters, the more positive psychological impacts they may experience. This is consistent with previous research that the amplification of stereotypes and lack of intersectional representation in media can lead to negative psychological outcomes for marginalized groups [@nolke_making_2018]. The findings suggest that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals given the high explanatory power.

The correlations between authenticity and intersectionality ratings and psychological impact scores also explain the disparities in psychological impacts among different LGBTQ+ subgroups, especially for sexuality. Regarding gender identity, authenticity rating has a stronger effect on psychological impact scores for men than women and other gender identity. This finding suggests that queer men may be more sensitive to whether media representations feel authentic or genuine. This sensitivity could stem from past experiences with harmful stereotypes or depictions such as ‘perfect homo’ of queer men in media. The lower psychological impact scores for queer men could also result from more existing queer men stereotypes in the media than women and other gender identities. Additionally, queer men respondents were less sensitive to intersectionality rating since there was a significant proportion of the data points featuring high intersectionality with low psychological impact scores. This suggests that queer men might prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities. Meanwhile, queer men who face fewer intersectional challenges may not feel represented by narratives that emphasize multiple forms of marginalization, leading to lower psychological benefit from such representations. Thus, the recent progress in queer media characters' intersectionality may result in more positive psychological impacts on women and other gender identities, as they were more invisible and marginalized before. This also applies to racial identity, where the intersectionality rating has a stronger effect on psychological impact scores for black, asian, and indian respondents than white respondents as they may have experienced more intersectional challenges in their lives. The higher psychological impact scores for racial minorities may also result from the recent increase in racial minority representation in queer media characters that feature more intersectional identities.

It is worth noting that authenticity and intersectionality ratings may also play a significant role in explaining the disparities in psychological impacts among different sexual orientations. Among all sexual orientations, only bisexual respondents had more data points condensed on the lower end of the authenticity rating and psychological impact scores. This suggests that bisexual respondents' low psychological impacts scores may be related to the perceived low authenticity of bisexual media characters. While bisexual men are often depicted as secretly gay with absence of bisexual representations, biseuxal women are often depicted as hypersexualized or fetishized [@young_why_2022]. This can further reinforce the stigma and stereotypes surrounding bisexuality as creedy or indecisive, perpetuating biphobia in society. The negative associations between intersectionality rating and psychological impact scores for asexual and pansexual men further indicated that queer men may prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities as there was barely any asexual or pansexual men in the media.

>>>>

  | The growing visibility of the LGBTQ+ community is accompanied by the flourishing of queer characters in media in the information era. While previous studies have explored the double-edged impact of queer media representation on LGBTQ+ individuals’ development, few have compared these effects across different LGBTQ+ subgroups. This study investigates queer media characters’ psychological impacts on LGBTQ+ individuals with different identities, examining the relationship between queer media consumption, perceived character authenticity, intersectionality, and queer characters' psychological impact scores using a reliable survey instrument in a worldwide sample.

  | Findings revealed that marginal groups within the LGBTQ+ community, including those from developing countries, gender minorities, and racial minorities, reported higher scores about queer media characters’ positive impacts on psychological well-being compared to their mainstream counterparts. However, in terms of sexual orientation, mainstream groups (i.e., gay and lesbian respondents) showed higher scores. Importantly, the study found strong positive correlations between authenticity ratings, intersectionality ratings, and scores of queer characters’ positive impacts on LGBTQ+ individuals' psychological well-being.

@@

The current study examined queer media characters’ impacts on LGBTQ+ individuals’ psychological well-being through two overarching research questions. The first research question investigated whether there were differences in queer characters’ psychological impacts among LGBTQ+ individuals with different identities. Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, racial identities, ages, and residential countries on queer characters’ psychological impacts. Given the fact that there were still absences of marginalized identities and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents). The second research question asked whether queer media consumption patterns, perceived character authenticity, and perceived character intersectionality can predict queer media characters’ psychological impacts. Specifically, this study hypothesized that lower exposure to queer media representations, and lower ratings for perceived character authenticity and intersectionality would result in lower ratings for queer characters’ positive psychological impact scores. Conversely, higher engagement with queer media representations, and higher ratings for perceived character authenticity and intersectionality would result in higher ratings for queer characters’ positive psychological impact scores.

@@

### Reliability Tests
Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (Table 1). Cronbach's alpha coefficients were calculated for each scale. Specifically, the authenticity rating measurement demonstrated satisfactory reliability (α = 0.76). The intersectionality rating measurement showed excellent reliability (α = 0.91). Both the media individual development scale and the media community belonging scale exhibited excellent reliability (α = 0.96 for both). The emotional well-being measurement also demonstrated excellent reliability (α = 0.96). Finally, the overall psychological well-being measurement showed the highest reliability with an excellent Cronbach's alpha of 0.98. These results indicate that all scales used in this study have good to excellent internal consistency, suggesting they are reliable measures of their respective constructs.

@@

### Respondent Characteristics
167 respondents were eligible for the data analysis after data cleaning. Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old. The average age of the sample was `r round(mean(queer.hypo$age), 1)` years old (*SD* = `r round(sd_age, 1)`). This wide age range ensured the study captured perspectives from individuals across different generations. Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective. Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as nonbinary, genderfluid, gender non-conforming, or agender. Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender. The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (Figure 2). The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native. This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersectional identities.

@@

One-way ANOVA results showed that there were no significant differences or directional effects in queer media characters’ psychological impacts among different generations (*p* = 0.70) or between transgenders and non-transgenders (*p* = 0.25). However, significant differences were found between developed and developing countries' residents (Figure 3). Specifically, residents in developed countries showed lower psychological impact scores by queer media characters than those in developing countries ($M_{\text{developed}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developed"]), 2)`$ vs. $M_{\text{developing}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developing"]), 2)`$; *F*(`r summary_country_effect$Df[1]`, `r summary_country_effect$Df[2]`) = `r round(summary_country_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_country_effect$"Pr(>F)"[1])`).

Though the ANOVA result did not show significant differences among different gender identities, there was a directional effect indicated by the violin plot (Figure 4). Specifically, men showed lower psychological impact scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs. $M_{\text{womenother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Women, or nonbinary, or agender"]), 2)`$; *F*(`r summary_gender_effect$Df[1]`, `r summary_gender_effect$Df[2]`) = `r round(summary_gender_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_gender_effect$"Pr(>F)"[1])`). The distribution also indicated that men have more low score distributions than their women or nonbinary counterparts. Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations. Nevertheless, there was also a directional effect (Figure 5). Specifically, bisexual individuals showed the lowest psychological impact scores among all sexual orientations, while gay or lesbian had the highest impact scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).

@@

Racial differences in queer media characters’ psychological impacts were marginally significant (Figure 6). Specifically, white respondents showed lower psychological impact scores than other racial groups ($M_{\text{white}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "White"]), 2)`$ vs. $M_{\text{blackother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "Black, Asian, Indian, and Others"]), 2)`$; *F*(`r summary_race_effect$Df[1]`, `r summary_race_effect$Df[2]`) = `r round(summary_race_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_race_effect$"Pr(>F)"[1])`).

```{r}
#| label: fig-plot-race-psych-impact
#| fig-cap: Racial Comparison of Queer Characters' Psychological Impacts
#| fig-width: 10
#| fig-height: 5
# Visualization: Violinplot
race_effect_boxplot <- ggplot(queer.hypo, aes(race_category, psychological_wellbeing_score)) + 
  geom_boxplot(aes(fill = race_category)) +
  theme_bw() +
  scale_fill_manual(values = c("#cfb5a0","#f1e2c8")) +               
  scale_colour_manual(values = c("#cfb5a0","#f1e2c8")) + 
  labs(title = "Racial Comparison of Queer Characters' Psychological Impacts", 
       x = "Racial Identity", y = "Queer Characters' Psychological Impact Score") +
  theme.clean()+
  theme(axis.text.x = element_text(hjust = 0.5))+
  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
  stat_summary(fun = mean, geom = "point", color = "white", size = 3, shape = 18, 
               position = position_dodge(0.75), aes(shape = "Mean"), 
               show.legend = FALSE) +  
  stat_summary(fun = mean, geom = "text", aes(label = round(after_stat(y), 2)), 
               color = "white", vjust = -1, position = position_dodge(0.75), 
               size = 4, show.legend = FALSE) +
  labs(fill = "Racial Identity")

@@

Figure 10 indicates that the authenticity rating positively predicts psychological well-being scores for all gender identities. The regression line for men is steeper, indicating that the authenticity rating has a stronger effect on psychological wellbeing scores for men. Nevertheless, given the fact that men have lower psychological impact scores, the authenticity rating may not be the only factor influencing psychological impact scores.

@@

Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations. It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low score distributions for both ratings. This result suggests that bisexual respondents' low psychological impacts scores may be related to the perceived authenticity of bisexual media characters.

@@

```{r}
#| label: fig-plot-auth-psych-impact-race
#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Racial Identity
#| message: false
#| fig-width: 11.5
#| fig-height: 5.5

@@

Linear regression results also indicated a significant effect of queer character intersectionality rating on psychological wellbeing impact scores (*F*(`r df1_inter`, `r df2_inter`) = `r round(f_statistic_inter, 2)`, *p* `r if(p_value_inter < .001) "< .001" else paste("=", round(p_value_inter, 3))`). The $R^2$ was `r round(r_squared_inter,3)`, indicating that the perceived queer character intersectionality explained `r round(r_squared_inter * 100, 1)`% of the variance in psychological wellbeing scores. This robust association suggests that LGBTQ+ individuals who perceive queer media characters as more intersectional and diverse tend to experience more positive psychological outcomes.

@@

```{r}
#| label: fig-plot-inter-psych-impact-country
#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Country
#| message: false
#| fig-width: 10
#| fig-height: 5

@@

The results of the study indicated that queer media characters' psychological impacts on LGBTQ+ individuals did not significantly differ among different generations. This finding suggests that queer media representations may have become more diverse in age over time, catering to different generations of LGBTQ+ individuals. It is also consistent with findings from @dhoest_queer_2022, which found that LGBTQ+ individuals across all generations were keen to watch LGBTQ-themed films and rated TV shows featuring LGBTQ+ characters as important. The recent years' increase in transgender media representation may have contributed to the positive psychological impacts on transgender respondents, resulting in the insignificant differences between transgender and non-transgender individuals. For instance, the number of transgender characters on broadcast TV increased from two characters in 2014 to 24 characters in 2024 [@GLAAD2024]. Reality shows such as *RuPaul's Drag Race* and TV series like *Pose* and *Euphoria* were also popular among transgender participants in this study.

The study has also found that queer media characters' psychological impacts on LGBTQ+ individuals were less significant for individuals living in developed countries than for those living in developing countries. A plausible explanation could be a higher saturation of queer characters in media leading to a normalization of queer identities in developed countries. As a result, the impact of individual characters may be less pronounced since audiences become desensitized to their presence. In contrast, the scarcity of queer characters in developing countries may lead to a more profound impact when they appear. Additionally, LGBTQ+ individuals in developed countries might have more access to mental health resources and support systems (e.g., LGBTQ+ advocacy groups), which could mitigate the effects of media representations on psychological well-being. Nevertheless, LGBTQ+ individuals in developing countries may rely more on cultural resources such as queer media characters for representation and community belonging, leading to a stronger psychological impact.

Regarding gender identity and racial identity, the study found that queer media characters' psychological impacts on LGBTQ+ individuals were more positive for gender and racial minorities. These findings reflect that queer media representations have become more diverse in gender and racial identities. Specifically, @GLAAD2024 reported 2024 as the fifth year there were more queer women than men on broadcast, with 58% women or nonbinary, and 42% men characters. Regarding racial identity, the number of LGBTQ+ characters of color on broadcast TV increased from 23% in 2014 to 50% in 2024, with 30% of LGBTQ+ characters being black, 7% Latine, 5% asian, and 8% multiracial or others. This shift in decades of LGBTQ+ representation may have contributed to the more positive psychological impacts on gender and racial minorities.

Nevertheless, the study found that regarding sexual orientation, the mainstream group (i.e., gay or lesbian) had the highest psychological impact scores, while bisexual respondents had the lowest. This is consistent with @GLAAD2024's report that the percentage of bisexual characters on broadcast TV was significantly lower than the percentage of bisexual as the majority in the LGBTQ+ community (24% vs. 58%). Apart from this disparity, the bi+ erasure (i.e., the tendency to not specify a character as bisexual) in media may have also contributed to the lower psychological impact scores of bisexual respondents. The following section further discusses the potential explanations from the perspectives of perceived character authenticity and intersectionality.

@@

This study found that the frequency of queer media exposure and discussion engagement may predict psychological impacts. Specifically, the results indicated that more respondents in developed countries had lower exposure to queer media characters (e.g., a few times per year), which may contribute to lower psychological impact scores. This finding suggests that the normalization of queer characters and more well-established social support systems for LGBTQ+ individuals in developed countries may have led to a desensitization effect, reducing the psychological impacts of queer characters. Regarding queer media discussion engagement, the results revealed that women and nonbinary individuals had higher discussion engagement than men, which may contribute to higher community belonging scores and overall psychological impact scores. This finding also highlights that there may not be enough online forums or platforms specifically tailored to the needs and interests of queer men. Additionally, social norms and expectations around masculinity may discourage queer men from openly discussing their experiences or engaging in vulnerable conversations that reveal their identities, resulting in lower community belonging scores.

The study also revealed that perceived queer character authenticity and intersectionality are strongly positively related to queer characters' psychological impact scores. The more authentic and intersectional LGBTQ+ individuals perceive queer media characters, the more positive psychological impacts they may experience. This is consistent with previous research that the amplification of stereotypes and lack of intersectional representation in media can lead to negative psychological outcomes for marginalized groups [@nolke_making_2018].

The correlations between authenticity and intersectionality ratings and psychological impact scores also explain the disparities in psychological impacts among different LGBTQ+ subgroups, especially for sexuality. Regarding gender identity, authenticity rating has a stronger effect on psychological impact scores for men than women and other gender identity. This finding suggests that queer men may be more sensitive to whether queer media representations feel authentic or genuine. This sensitivity could stem from past experiences with harmful stereotypes or depictions such as ‘perfect homo’ of queer men in the media. The lower psychological impact scores for queer men could also result from more existing queer men stereotypes in the media than women and other gender identities. Additionally, queer men respondents were less sensitive to intersectionality rating since there was a significant proportion of the data points featuring high intersectionality with low psychological impact scores. This suggests that queer men might prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities. Thus, the recent progress in queer media characters' intersectionality may result in more positive psychological impacts on women and other gender identities, as they were more invisible and marginalized before. This also applies to racial identity, where the intersectionality rating has a stronger effect on psychological impact scores for black, asian, and indian respondents than white respondents as they may have experienced more intersectional challenges in their lives. The higher psychological impact scores for racial minorities may also result from the recent increase in racial minority representation in queer media characters that feature more intersectional identities.

It is worth noting that authenticity and intersectionality ratings may also play a significant role in explaining the disparities in psychological impact among different sexual orientations. Among all sexual orientations, only bisexual respondents had more data points condensed on the lower end of the authenticity rating and psychological impact scores. This suggests that bisexual respondents' low psychological impacts scores may be related to the perceived low authenticity of bisexual media characters. While bisexual men are often depicted as secretly gay with absence of bisexual representations, biseuxal women are often depicted as hypersexualized or fetishized [@young_why_2022]. This can further reinforce the stigma and stereotypes surrounding bisexuality as greedy or indecisive, perpetuating biphobia in society. The negative associations between intersectionality rating and psychological impact scores for asexual and pansexual men further indicated that queer men may prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities as there was barely any asexual or pansexual men in the media.

## Conclusion
This study investigates the psychological impacts of queer media characters on LGBTQ+ individuals across different subgroups and identifies predictors of these impacts. The findings indicate that while queer media characters' psychological impacts did not significantly differ among different generations and transgender status, they were more positive for individuals living in developing countries, women and nonbinary individuals, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years. The study also reveals that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals. While queer men may be more sensitive to authenticity due to existing stereotypes, queer women and other identities tend to benefit more from intersectional representations. Additionally, bisexual individuals may experience lower psychological impacts due to the lack of authentic bisexual representations in the media. The current study enriches the understanding of different LGBTQ+ individuals' needs for queer media characters by comparative analysis, revealing the necessity for the media industry to provide LGBTQ+ audience with more authentic and diverse queer representations. It is also necessary to present bisexual characters in a non-stereotypical way to reduce biphobia and increase bisexual individuals' psychological well-being. The limitations of this study lie in the relatively small sample size, disproportionate representation of different subgroups, and the lack of comparison among different media’s impacts. Future research may consider a larger sample with more balanced representation of different subgroups to further explore the psychological impacts of queer media characters on LGBTQ+ individuals. Scholars may also be interested in the intersectional analysis of different media’s impacts.
